Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-08-11 tex/Main Text/manuscript.tex
初步写完结果和讨论

\subsection*{Causes of water utilization regime changes}
Some main drivers caused the changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are key to the
changes in the tendentiousness of water utilization in P1 and P2.
During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
and agriculture was the dominant water use (xx \% of the total).
After entering P2 to P3, however, while the expansion of irrigated area stalled, 
industry and services gradually took off, which took up more water resources.
% 用水关系的变化
(2) Efficiency of water use sparkly changed during the P3.
Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
both their output per unit and water consumption per unit area experienced significant declines.
% 不断变化的管理模式。
(3) Changing water management practice contributed between different periods.
In P1, most of the reservoirs are built in regions where water use is growing, 
and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
In P2, on the other hand, the number of additional reservoirs decreases significantly. 
In P3, the number of reservoirs increases significantly again, 
but the growth of storage capacity does not match the growth of water demand.

@@

\subsection*{Transition Framework}
Tables should be included in the main manuscript file and should not be uploaded separately.

@@

\subsection*{Development Traps}

>>>>

\subsection*{Causes of water utilization regime changes}
Some main drivers caused the changes of water utilization regime.
% 经济总量提升导致资源耗竭的加速。
(1) The expansion of irrigated area and the economic growth of industry and services are key to the
changes in the tendentiousness of water utilization in P1 and P2.
During P1, irrigated agricultural area in the Yellow River basin expanded rapidly at a rate of xx/year, 
and agriculture was the dominant water use (xx \% of the total).
After entering P2, however, while the expansion of irrigated area stalled, 
industry and services gradually took off, which took up more water resources.
% 用水关系的变化
(2) Efficiency of water use sparkly changed during the P3.
Although both industrial services output and irrigated agricultural area resumed expansion in P3, 
both their output per unit and water consumption per unit area experienced significant declines.
As a result, after the P3, the proportions of the different water-using sectors tend to average out 
while the total water consumption remains stable.
% 不断变化的管理模式。
(3) Changing water management practice contributed between different periods.
In P1, most of the reservoirs are built in regions where water use is growing, 
and the trend of growth in storage capacity and growth in water demand remain relatively consistent regionally.
In P2, on the other hand, the number of additional reservoirs decreases significantly. 
Within P3, the number of reservoirs increases significantly again, 
but the growth of storage capacity does not match the growth of water demand.

@@

\subsection*{Transition Framework}
% 普遍存在的稳态转换可以由渐变或突变造成，而人类压力在世界范围内都是稳态转换最重要的驱动因素之一。
Widespread regime shift of coupled systems can be caused by gradual or abrupt changes, 
where anthropogenic stresses are among the most important drivers of. 
% 而随着人类干预的加深，水循环出现了自然-社会二元结构，主导当前人水系统的互馈过程。
With the accumulation of human interventions, 
a natural-social binary structure of the water cycle has emerged, 
dominating the current feedbacks of the human-water systems.
% 我们的研究结果表明，与社会-生态系统的过渡过程类似，水资源利用体系的变化也存在类似稳态转换的阶段性特征，并最终呈现出自然-社会二元结构。
According to our results, 
regime shifts as transitional phases of water utilization regimes, 
similar to evolution of social-ecological system, 
is one of the most important characteristics towards natural-social binary structure.
% 因此，我们在总结黄河流域变化过程的基础上，进一步概念化了水资源利用制度的过渡框架。
As such, we summarized a transition framework of the water utilization regimes, 
which conceptualizes a general trajectory towards a natural-social binary water cycle (figure \ref{fig:framework}).

@@

% 在水循环向二元系统过渡过程中，存在几个明显的特征。
Towards natural-social binary cycle, there are two obvious features between different transition phases.
% 阶段1
From the first phase (natural cycle) (Figure~\ref{fig:framework}a), 
water is a kind of direct provisioning resources, mainly supporting to crop, livestocks or human-beings, 
as basic ecological services.
% 阶段2
However, to the second phase (local binary cycle) (Figure~\ref{fig:framework}b), 
as local socio-economic systems developing, 
industry and services (secondary and tertiary-industry) calling for further water consumptions.
However, since their services can only be generated through the circulation of socio-economic systems, 
water resources play a non-provisioning role in this cycle. 
What's more, better organized socio-economic system and developed technology 
gives humans the will and ability to better manage water resources and change, 
with intensive intervention in the natural water cycle. 
% 阶段3
Entering the third phase (basin binary cycle) (Figure~\ref{fig:framework}c), 
with further growth in more economically efficient industries and services, 
trade-off between whose water demands with provisioning demands 
should be based on the needs of regional socio-economic systems.
What's more, Water withdrawals are no longer simply determined by local economic development, 
but more so by the socio-economic development needs of the entire basin, 
while water resource management are also more often considered on a basin-wide basis, correspondingly.

% 水资源利用制度包括压力、倾向性、格局三个重要因素，三个指标在过渡框架中随着不断变化。
Throughout the above transition phases towards binary water cycle, 
three dimensions of water utilization regime are various, following three laws of evolution respectively.
Firstly, although stresses on water resources increases by economic expansion boosting water demands, 
socio-economic progress responding to resource scarcity because of better management and increased water use efficiency. 
For Example...
Secondly, the non-provisioning part of water demands further growths and 
tendentiousness of water utilization continually changes, 
as humans are more dependent on benefits from non-provisioning part of water supply.
Thirdly, With closer socio-economic ties between regions and between regions and river basins, 
the geographic scope of resource supply and demand allocation is expanding, 
leading to changing patterns of water utilization.
By combining the three dimensions, water utilization regimes have a tendency of transitional evolution.

% 综上所述，社会对水资源的利用模式作为一个人-水互馈系统，存在阶段性过渡特征。
For the Yellow River Basin, 
In addition to the Yellow River Basin, which is the focus of this study, 
human-water relations in major river basins around the world 
can be explained by the phases of the transitional framework.
For examples, \dots \dots.
In summary, our proposed transitional framework for the nature-society binary water cycle is general in nature.

\subsection*{Development Traps}
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
Since each basin at different transition phase, 
they are facing different development traps regarding water utilization, 
leading an unsustainable trajectory. 
Like social-ecological systems and other complex systems, 
coupled human-water system disintegrate may occurred under the gradual pressure of rising resources, 
or collapse emerged because of structural mismatches.
A number of studies have identified transformation as an important way out of unsustainable trajectory, 
and different types of transformation are required according to dominating phases and traps of systems.
Thus, it is crucial to distinguish major development traps 
based on the transition framework of water utilization regimes.

% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to case studies from watersheds around the world, 
big river basins often face a resource trap at the beginning of their development, 
while highly developed ones often face a structural trap.
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
For the Yellow River Basin, 
after the successive expansion of agriculture and industrial services during the P1 and P2 phases, 
the utilization rate of surface water resources has reached 80\% of the natural runoff, 
far exceeding the internationally recognized threshold of 40\%.
Although water management measures in P1 (construction of numerous reservoirs) 
mitigated the pressure on water resources due to accelerated development, 
the pressure on water resources rebounded rapidly during P2, 
when the number of new reservoirs declined significantly.
These have led to increasingly severe outages and groundwater depletion of the Yellow River from P2 onwards, 
and the Yellow River basin had been in a notable resource trap.
% 资源困局可能普遍存在
In any case, the xxx and xxx basins have a development history similar to that of the Yellow River, 
suggesting that resource distress may be widespread in the early stages of the transition.

% 后来摆脱了资源陷阱（表现形式 xxx）。
Faced with a clear resource trap, a clear transformation path towards integrated basin management was proposed
that has contributed to the gradual escape of the Yellow River from the resource trap.
.....
In short, these integrated management practices made the utilization of water resources into a regime of unified scheduling, 
in the Yellow River Basin 
to escape from the “resource trap” of economic expansion and accelerated resource depletion.
Similarly, 
many of the world's major river basins have eventually moved towards a system of integrated management and integrated dispatch, 
especially the XXX and XXX basins, 
where water resources are extremely scarce.

% 展望：未来还可能陷入结构陷阱，（表现形式：用水效率悖论的同时，灵活性进一步降低，
However, Despite achieving integrated management and escaping through increased water efficiency, 
basins still face new structural traps and require further transformation.
Firstly, in line with paradox of irrigation efficiency \ref{graftonParadoxIrrigationEfficiency2018}, 
significant improvement in agricultural irrigation efficiency (or decline in water use intensity) 
has been accompanied by a resurgence in irrigated area, 
resulting in an unabated and weak upward trend in water stress.
% 水资源压力仍在增大，而节水能力已经进入瓶颈，倾向性贡献减少）
As integrated basin allocation dominates water allocation, 
the propensity to allocate water between non-supply industries, such as industrial services, 
and agriculture is becoming fixed.
At the same time, the flexibility of water use is declining since domestic water use and thermal water use growth rapidly. 
Typically, similar to other cases, these may lead to a reduction in watershed resilience 
and leave highly coupled human-water systems facing greater vulnerability to collapse 
-- a typically structural trap.
% 下一步：可以通过统一调控，调整格局来调整结构，突破结构陷阱。
% 总结：整个流域需进一步转型与适应，以实现高质量发展。
Therefore, based on the identification of the current basin transition stage and development dilemma, 
further transitional governance is still needed to achieve high-quality sustainable development of the basin.
